---
title: "AF3Input"
author: "Peter Huang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{AF3Input}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

AF3Input converts tabular DNA candidate calls into AlphaFold 3 input JSON.
The sequence column is configurable, and selected metadata columns can be
preserved in the DNA entity description.

## Create JSON from a candidate table

```{r create-json}
library(AF3Input)

candidates <- read_candidate_table(
    system.file("extdata", "g4_candidates.tsv", package = "AF3Input")
)

paths <- write_af3_jsons_from_table(
    candidates,
    out_dir = tempdir(),
    sequence_col = "SEQUENCE",
    description_cols = c("ID", "POSITION", "SCORE", "ABS_SCORE"),
    name_cols = c("ID", "POSITION"),
    score_col = "SCORE",
    reverse_complement_negative = TRUE,
    ions = list(list(code = "K", copies = 2)),
    seeds = c(1, 2),
    limit = 2
)

basename(paths)
```

Negative-score rows can be reverse-complemented before writing JSON. This is
useful for G4Hunter-like output where negative scores often mark C-rich
sequences whose reverse complement is G-rich.

```{r session-info}
sessionInfo()
```
